\documentclass[a4paper,12pt]{report}
\usepackage[top=3cm,bottom=3cm,left=3.7cm,right=3cm]{geometry}
\usepackage{setspace}
\doublespacing
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{url}
\usepackage{marvosym}
\usepackage{color}

\begin{document}

\include{title_1}
\include{title_2}

\begin{abstract}
  The role of actively moving boundary layer is very interesting in drag reduction. This project is focused on investigation of turbulent statistics in moving boundary layer. The model used in this project is flat plate with spanwise oscillating movement. To obtain a better insight on the turbulence statistics, Direct Numerical Simulation is used to model the fluid flow.

  In this project, the effect of the surface movement pattern toward drag reduction is observed. The turbulence statistics of interest are velocity profile, turbulence intensities and skin-friction coefficient. To gain a better insight on the moving pattern, comparison is done with related project with different moving pattern.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
  I would like to express my gratitude to the following individuals who have involved in the process of finishing this project, directly and indirectly.
\begin{itemize}
  \item Asst. Prof. Martin Skote for all of his guidances and supervisions to complete this project. I am very grateful because he is willing to work together with me who came to him as a stranger. 
  \item My parents, brother and sister who have supported my decision to join this course. 
  \item Some of classmates in MSc in Aerospace Engineering program.
  \item Last but not least, I would like to express my gratitude to free software and open source communities. This project is completely done by using open source and free softwares. This report was written by using {\bf \LaTeX} in {\bf GNU Emacs}. All the figures were generated by {\bf gnuplot} and the data analysis was done in {\bf GNU Octave}. Ultimately, the whole project was done in {\bf Ubuntu Linux}. Free as in the freedom of speech!!! 
\end{itemize}
\end{abstract}

\pagenumbering{roman}
\tableofcontents
\listoffigures
\listoftables
\pagenumbering{arabic}

\include{chapter_1}
\include{chapter_2}
\include{chapter_3}
\include{chapter_4}
\include{chapter_5}
\include{chapter_6}

\begin{thebibliography}{2}
\bibitem{viotti} Claudio Viotti, Maurizio Quadrio and Paolo Luchini, ''Streamwise oscillation of spanwise velocity at the wall of a channel for turbulent drag reduction''. \emph{Physics of Fluids 21}, 115109, 2009.
\bibitem{indra} Indra Yudisthira, ''Turbulent Structures and the Formation of Drag in a Turbulent Boundary Layer''
\bibitem{JB} John J. Bertin and Russell M. Cummings,\emph{Aerodynamics for Engineers, 5th edition.} Prentice Hall, 2009.
\bibitem{JA} John D. Anderson Jr., \emph{Fundamentals of Aerodynamics, 4th edition.} McGraw-Hill, 2007.  
\bibitem{PK} Pijush K. Kundu and Ira M. Cohen, \emph{Fluid Mechanics, 3rd edition.} Elsevier, 2004.
\bibitem{Wiki} \emph{Computational Fluid Dynamics}. \url{http://en.wikipedia.org/wiki/Computational_fluid_dynamics} (Last visited on 6 September 2010)
\bibitem{FVM} \emph{Finite volume}. \url{http://www.cfd-online.com/Wiki/Finite_volume} (Last visited on 28 September 2010).
\bibitem{FEM} \emph{Finite element method}. \url{http://en.wikipedia.org/wiki/Finite_element_method} (Last visited on 28 September 2010).
\bibitem{parviz} Parviz Moin and Krishnan Mahesh. ''Direct Numerical Simulation: A Tool in Turbulence research''. \emph{Annual Review in Fluid Mech.}, 30:539-78, 1998.
\bibitem{ferziger} Joel H Ferziger and Milovan Peric, \emph{Computational Methods for Fluid Dynamics 3rd edition}. Springer, 2002.
\bibitem{chung} Chung T. J., \emph{Computational Fluid Dynamics}. Cambridge University Press, 2002.
\bibitem{canuto} C. Canuto, M. Y. Husaini, A. Quarteroni, T. A. Zang, \emph{Spectral Methods: Fundamentals in Single Domains}. Springer, 2006.
\bibitem{boyd} J. P. Boyd, \emph{Chebysev and Fourier Spectral Methods, 2nd edition}. Dover Publications, 2001.
\bibitem{Simson} Mattias Chevalier, Philipp Schlatter, Anders Lundbladh and Dan S. Henningson, ''Simson User Guide v4.0'', Stockholm, Sweden, Technical Report, 2007.
\bibitem{Jung} W. J. Jung, N. Mangiavacchi, and R. Akhavan, ''Suppresion of turbulence in wall-bounded flows by high-frequency spanwise oscillations'', \emph{Physics of Fluid A: Fluid Dynamics}, vol. 4, no. 8, pp. 1605 -- 1607, 1992. 

\bibitem{skote-1} Martin Skote, Dan S. Henningson and Ruud A. W. M. Henkes, ''Direct numerical simulation of self similar turbulent boundary layers in adverse pressure gradients'', \emph{}
\bibitem{skote-2} Ruud A. W. M. Henkes, Martin Skote, adn Dan S. Henningson, ''Application of turbulence models to equilibrium boundary layers under adverse pressure gradients'', \emph{}

\end{thebibliography}

\appendix
\include{appendix_1}
\include{appendix_2}

\end{document}
